---
title: <br><br><center>AVIANCE GROUP<center>
author: "Cutting Edge Events"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r knitr_init, echo=FALSE, cache=FALSE, message= FALSE,warning=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=750)
```


```{r echo=FALSE, message=FALSE,warning=FALSE}
library(readxl)
library(shiny)
library(dplyr)
library(knitr)
```

## WALKING DISTANCE RESTAURANTS{.tabset .tabset-fade .tabset-pills}

### Alba Granados

Alba Granada reopens its doors in 2016 with a completely renewed look. The spacious restaurant is divided into two floors: it has an elegant dining room on the ground floor and a fantastic New York style cocktail bar on the first floor, plus an exquisite balcony. Its cuisine is traditional based with current touches and shares prominence with its extensive wine cellar. 

<style>
p.comment {
background-color: #ffcc99;
padding: 10px;
border: 1px solid black;
border-radius: 5px;
}
</style>

<p class="comment">
The basic menu is about starters to share, a main course to choose, dessert and drinks included (2 glasses of wine per person, water and coffee) Rates from 51€.</p>


**Distance to the hotel**: 15 minutes by walking

<img src = "https://u.tfstatic.com/restaurant_photos/827/4827/169/612/alba-granados-alba-granados-1-cd668.jpg" width="720"> 

<img src = "https://u.tfstatic.com/restaurant_photos/827/4827/169/612/alba-granados-alba-granados-3-7af7b.jpg" width="720">


### Toto

Toto restaurant & wine bar is the new hot spot in Barcelona. A space boasting a spectacular design where good taste is combined with excellent Italian-inspired cuisine with seasonal products of proximity -slow cook-.

<style>
p.comment {
background-color: #ffcc99;
padding: 10px;
border: 1px solid black;
border-radius: 5px;
}
</style>

<p class="comment">
The basic menu includes starters to share, a main course to choose, dessert and drink package (1/4 bottle of wine per person water and coffee) Rates from 54€.</p>

**Distance to the hotel**: 15 minutes by walking

<img src = "http://barcelona.lecool.com/files/2013/06/toto.jpg" width="720"> 

<img src = "https://www.chefcaprabo.com/export/shared/.galleries/noticias/3226001CAS_682x433.png_908605617.png" width="720">

### Flamant

Decorated like an old house and with different dining rooms, Flamant is a huge restaurant that offers excellent season cuisine with Mediterranean and international influences. Here they work carefully on the presentation of their dishes.
Flamant is a large restaurant with capacity for more than 200 people that presents a quite old-fashioned space with restored furniture and natural sunlight.

<style>
p.comment {
background-color: #ffcc99;
padding: 10px;
border: 1px solid black;
border-radius: 5px;
}
</style>

<p class="comment">
3 main courses to choose. Drink package included(1/2 bottle of wine per person, water, soft drinks and coffee). Rates from 35€</p>


**Distance to the hotel**: 10 minutes by walking

<img src = "https://u.tfstatic.com/restaurant_photos/075/11075/169/612/6a03ec2249db2ef5e12a4ba49551b400.jpg" width="720">

<img src = "https://www.atrapalo.com/common/photo/res/33118/175492/ticr_0_0.jpg" width="720">

### Julivert Meu

Julivert Meu is an old Catalan farmhouse transported to the Barcelona's city center. A restaurant working since 1970. They offer an excellent traditional and homemade food, they represent the best of Catalan gastronomy and the spirit of good eating.

<style>
p.comment {
background-color: #ffcc99;
padding: 10px;
border: 1px solid black;
border-radius: 5px;
}
</style>

<p class="comment">
Menu: includes a classic catalan starters to share, a main course to choose, dessert and drink package (wine, sangría, water and coffee). Rates from 35€</p>

**Distance to the hotel**: 6 minutes by walking

<img src = "https://media-cdn.tripadvisor.com/media/photo-s/0e/db/8a/f7/ready-for-lunch.jpg" width="720"> 

<img src = "https://u.tfstatic.com/restaurant_photos/269/310269/169/612/julivert-meu-julivert-meu-7-a2c36.jpg" width="720">

## LAST NIGHT - ALTERNATIVE RESTAURANTS{.tabset .tabset-fade .tabset-pills}

### Xalet de Montjuïc

Located in an idyllic setting on the top of the Montjuïc hill, El Xalet is a spectacular restaurant that offers the best views over Barcelona from its dining rooms and wonderful panoramic terraces. Exquisite and modern in its design, the restaurant presents, in a select and refind atmosphere, signature Mediterranean and Catalan cuisine. 

The restaurant is spread out over three levels. The one upper one has a bar, a cosy dining room and a wonderful terrace.

<style>
p.comment {
background-color: #ffcc99;
padding: 10px;
border: 1px solid black;
border-radius: 5px;
}
</style>

<p class="comment">
Menu: 3 courses menu including drink package (wine, water and coffee). Rates from 76€</p>

**Bus transfer is required**

<img src = "https://www.gruptravi.com/wp-content/uploads/EasyRotatorStorage/user-content/erc_31_1396539645/content/assets/T-E-R-R-0.png" width="720">

<img src = "https://www.gruptravi.com/wp-content/uploads/EasyRotatorStorage/user-content/erc_31_1396539645/content/assets/Xalet-Sunset-0.jpg" width="720">

### Mirabe

For over a decade, at the end of Avenida Tibidabo a splendid balcony over Barcelona offers a spectacular setting to enjoy the best views of the city. Mirabé is a very special place ideal for watching the sunset, ejoying a nice dinner or having a good gin and tonic. 

Elegant and warm, the top floor of the space has a large window with a long bar that offers a stunning view of the city. 

<style>
p.comment {
background-color: #ffcc99;
padding: 10px;
border: 1px solid black;
border-radius: 5px;
}
</style>

<p class="comment">
Menu: Welcome aperitive and 3 main courses. It also includes drink package (2 glasses of wine per person, water, soft drinks and coffee) Rates from 55€</p>

<img src = "https://u.tfstatic.com/restaurant_photos/738/46738/169/612/mirabe-sala-b0c01.jpg" width="720">

<img src = "https://u.tfstatic.com/restaurant_photos/738/46738/169/612/mirabe-sala-0e63b.jpg" width="720">


## MAP


```{r echo=FALSE, warning=FALSE, message=FALSE}

library(leaflet)
library(stringr)
library(ggmap)
library(readxl)
library(dplyr)
library(leaflet.extras)
library(shiny)

coordinates <- read_excel("timeline.xlsx", 
    sheet = "Sheet3", col_types = c("text", 
        "text", "numeric", "numeric", "text", 
        "text"))

coordinates$Category <- factor(coordinates$Category)

m <- coordinates %>% 
  leaflet(options = leafletOptions(dragging = TRUE,
  minZoom = 12, maxZoom = 18)) %>% 
  addProviderTiles("Esri") %>% 
  setView(lng = 2.1687300, lat = 41.3863900, zoom = 14) 

pal <- colorFactor(palette = c("red","blue"),
      levels = coordinates$Category)

m %>% clearBounds() %>% 
  addCircleMarkers(radius = 5, color = ~pal(Category)) %>% 
  addPopups(popup = paste0("<b>",coordinates$Location,"</b>")) %>% 
  addLegend(position = "bottomright", pal = pal, 
  values = coordinates$Category) %>% addResetMapButton()

```


*****

## Terms & Conditions

  * Rates valid for 2019.
  
  * For a group of minimum 15 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  
*****



